Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-19 paper/main.tex
Transcribe discussion outline as it is now

>>>>

Outline:
\begin{enumerate}
\item Speech is new
\item No frame-wise info, but high-level cinematographic semantics -- however, only for the movie stimulus
\item Conclusion: stimuli are suitable, and on-par for conventional ones
\item Compare the naturalistic results with each other, anterior bias (already hint on audio localizer)
\item issues with visual model, call for more confounds
\item how different from aziz?
\item impact of no task?
\item particular composition of audio contrast vs optimal visual stimuli
\item compare audio results to block-design localizer, again anterior bias, not an averaging effect
\item cite poldrack2007 to state that the procedure in sengupta was better, but we nevertheless did not do it...
\item actual discussion of anterior bias
\item other results RSC LOC
\item concluding statement
\end{enumerate}
